Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2021-04-10 gtsummary_submission.tex
overleaf

While other R packages are available to clean and present summary statistics and regression results in statistical reports, \pkg{gtsummary} is unique in that it is a one-stop-shop for most types of statistical tables and offers diverse features to customize content of tables to a high degree. It also includes the ability to report statistics from the tables inline in an RMarkdown report.
%For example with \CRANpkg{finalfit}, you have to manually specify a printing engine for the table to render.
%Furthermore, \CRANpkg{tableone} reports on general descriptive statistics, but it is lacking in its ability to produce tables for regression modeling strategies in R.

@@

% adding table describing trial dataset
\input{tbl_trial_desc.tex}

@@

% code for tbl_summary() with arguments
\input{tbl_tbl_summary_args.tex}

@@

% code for tbl_summary() with arguments
\input{tbl_tbl_summary_family.tex}

@@

% adding table describing fns for customization
\input{tbl_modify.tex}

>>>>

While other R packages are available to clean and present summary statistics and regression results in statistical reports, \pkg{gtsummary} is unique in that it is a one-stop-shop for most types of statistical tables and offers diverse features to customize content of tables to a high degree. It also includes the ability to report statistics from the tables inline in an RMarkdown report.
For example other summary statistics packages such as \CRANpkg{skimr}, \CRANpkg{summarytools}, and \CRANpkg{tableone} provide detailed descriptive statistics, but at least one major advantage of \CRANpkg{gtsummary} is the ability to also provide these same descriptive statistics that are publication ready in a scientific journal with little or no additional formatting.
Additionally \CRANpkg{gtsummary} has specific internal algorithms to identify variable data types so the user does not have to specify if a variable should be displayed with categorical or continuous summaries, unlike  \CRANpkg{tableone}.
However, it is possible to override \CRANpkg{gtsummary} variable selection defaults if the users chooses too. 
%For example with \CRANpkg{finalfit}, you have to manually specify a printing engine for the table to render.
%Furthermore, \CRANpkg{tableone} reports on general descriptive statistics, but it is lacking in its ability to produce tables for regression modeling strategies in R.

@@

% adding table describing trial dataset
\input{tex_tables/tbl_trial_desc.tex}

@@

% code for tbl_summary() with arguments
\input{tex_tables/tbl_tbl_summary_args.tex}

@@

% code for tbl_summary() with arguments
\input{tex_tables/tbl_tbl_summary_family.tex}

@@

% adding table describing fns for customization
\input{tex_tables/tbl_modify.tex}
